exp1_lik_by_trial

### 2020-09-09 exp1_lik_by_trial.Rmd
added posterior plots

library(dplyr)
```

@@

# Prepping data for Bayesian code
dat <- as_tibble(dat) %>% group_by(human_id,game)
dat <- dat %>%
  mutate(ai_action_prev = lag(ai_action,1), human_action_prev = lag(human_action,1))

@@

dat <- as.data.frame(dat)                       
exp1_lik_by_trial <- data.frame()

@@

  # QLS likelihoods 
  pars_QLS <- unlist(filter(optim_results, ID == id)%>%select(QL_states_Beta,QL_states_alpha))
  QLS_lik <- Q_learn_states(pars_QLS ,tdat,"likelihood_by_trial",gamma = 0)

  # Bayes model no transfer likelihoods
  theta_NT <- unlist(filter(optim_results, ID == id)%>%select(theta_no_transfer))
  Bayes_NT_lik <- exp1_Bayes_model_LL(theta_NT ,tdat, generalize = "no", "likelihood_by_trial")

  # Bayes model with Transfer likelihood
  theta_Tr <- unlist(filter(optim_results, ID == id)%>%select(theta_transfer))
  Bayes_Tr_lik <- exp1_Bayes_model_LL(theta_Tr ,data = tdat, generalize = "game", "likelihood_by_trial")

  exp1_lik_by_trial <- rbind(exp1_lik_by_trial,
                        data.frame(
                          "human_id" = id,
                          "condition" = dat$condition,
                          "game" = dat$game,
                          "round" = dat$round,
                          "QLS_lik" = QLS_lik,
                          "Bayes_NT_lik" = Bayes_NT_lik,
                          "Bayes_Tr_lik" = Bayes_Tr_lik
                        ))
  #cat(as.character(Bayes_Tr_lik[c(1,51,101)]))
}

@@

For

@@

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)

mean_lik <- exp1_lik_by_trial %>%
  select(human_id,condition,game, round,QLS_lik,Bayes_NT_lik,Bayes_Tr_lik) %>%
  group_by(condition,game,round) %>%
  summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
            mean_NT_lik = mean(Bayes_NT_lik, na.rm = TRUE),
            mean_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))

mean_lik$game <- factor(mean_lik$game,levels=c("rps","fwg","numbers"))

data_long <- gather(mean_lik, strategy, probability, mean_QLS_lik:mean_Tr_lik, factor_key=TRUE)

>>>>

library(dplyr)
library(ggplot2)
```

@@

#Prepping data for Bayesian code
dat <- as_tibble(dat) %>% group_by(human_id,game)
dat <- dat %>%
  mutate(ai_action_prev = lag(ai_action,1), human_action_prev = lag(human_action,1))

@@

```{r}
dat <-as.data.frame(dat)
exp1_lik_by_trial <- data.frame()

# dat%>% group_by(human_id) %>%
#   mutate(pars_QLS = as.vector(optim_results%>% dplyr::select(QL_states_Beta,QL_states_alpha))) %>%
#   mutate(QLS_lik = Q_learn_states(pars_QLS[1,] ,tdat,"likelihood_by_trial",gamma = 0))

@@

  # QLS likelihoods 
  pars_QLS <- as.vector(filter(optim_results, ID == id)%>% dplyr::select(QL_states_Beta,QL_states_alpha))
  tdat$QLS_lik <- Q_learn_states(pars_QLS ,tdat,"likelihood_by_trial",gamma = 0)

  #Bayes model no transfer likelihoods
  theta_NT <- unlist(filter(optim_results, ID == id)%>% dplyr::select(theta_no_transfer))
  tdat$Bayes_NT_lik <- exp1_Bayes_model_LL(theta_NT ,data = tdat, generalize = "no", "likelihood_by_trial")

  # Bayes model with Transfer likelihood
  theta_Tr <- unlist(filter(optim_results, ID == id)%>% dplyr::select(theta_transfer))
  tdat$Bayes_Tr_lik <- exp1_Bayes_model_LL(theta_Tr ,data = tdat, generalize = "game", "likelihood_by_trial")

  exp1_lik_by_trial <- dplyr::bind_rows(exp1_lik_by_trial,tdat)

  # 
  # exp1_lik_by_trial <- rbind(exp1_lik_by_trial,
  #                       data.frame(
  #                         "human_id" = id,
  #                         "condition" = dat$condition,
  #                         "game" = dat$game,
  #                         "round" = dat$round,
  #                         "QLS_lik" = QLS_lik,
  #                         "Bayes_NT_lik" = Bayes_NT_lik,
  #                         "Bayes_Tr_lik" = Bayes_Tr_lik
  #                       ))
  #cat(as.character(Bayes_Tr_lik[c(1,51,101)]))
}

@@

@@

mean_lik <- exp1_lik_by_trial %>%
  select(human_id,condition,game, round,QLS_lik,Bayes_NT_lik,Bayes_Tr_lik) %>%
  group_by(game, condition, round)  %>%
  dplyr::summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
            mean_NT_lik = mean(Bayes_NT_lik, na.rm = TRUE),
            mean_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))

data_long <- tidyr::gather(mean_lik, strategy, probability, mean_QLS_lik:mean_Tr_lik, factor_key=TRUE)
